New Windows Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations

### 2019-12-22 nontex/install/linux/fn_ubuntu.Rmd
git multi repo no passphrase initialize

---
title: "Atom, Git, Github, etc Set-up for Linux"
output:
  pdf_document:
    df_print: paged
    number_sections: true
  html_notebook:
    number_sections: true
  word_document:
    number_sections: true
  html_document:
    number_sections: true
urlcolor: blue
always_allow_html: yes
---

Go back to [fan](http://fanwangecon.github.io/)'s [Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/nontex/).

@@

```{bash}
# install git
sudo apt-get install git
# generate repo directory and sync
mkdir ~/PyFan
cd ~/PyFan
git init
git config --global user.name "Fan Wang"
git config --global user.email wangfanbsg75@live.com
git remote add github git@github.com:FanWangEcon/PyFan.git
git pull github master
```

>>>>

---
title: "Example and Tutorial for Atom, Git, Github, etc Set-up for Linux"
output:
  pdf_document:
    df_print: paged
    number_sections: true
  html_notebook:
    number_sections: true
  word_document:
    number_sections: true
  html_document:
    number_sections: true
urlcolor: blue
always_allow_html: yes
---

Go back to [fan](http://fanwangecon.github.io/)'s [Tex4Econ and Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/).

@@

```{bash}
# install git
sudo apt-get install git
# generate repo directory and sync
mkdir ~/PyFan
# mkdir fanwangecon.github.io PyFan Tex4Econ R4Econ M4Econ Py4Econ Teaching
cd ~/PyFan
git init
# git config only needs to happen once, info stored under ~/.gitconfig
git config --global user.name "Fan Wang"
git config --global user.email wangfanbsg75@live.com
git remote add github git@github.com:FanWangEcon/PyFan.git
git pull github master
```

### 2019-12-22 nontex/install/windows/fn_installations.Rmd
git multi repo no passphrase initialize

---
title: "Python and R set-up and Installations on New Computer"
output:
  pdf_document:
    df_print: paged
    number_sections: true
  html_notebook:
    number_sections: true
  word_document:
    number_sections: true
  html_document:
    number_sections: true
urlcolor: blue
always_allow_html: yes
---

Go back to [fan](http://fanwangecon.github.io/)'s [Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/nontex/).

@@

See Anaconda Installation Directory, in anaconda prompt:
```{bash}
where anaconda
# C:/ProgramData/Anaconda3/Scripts/anaconda.exe
where python
# C:/ProgramData/Anaconda3/python.exe
where jupyter
# C:/ProgramData/Anaconda3/Scripts/jupyter.exe
where jupyter-kernelspec
# if R installed already
where r
```

@@

```{r}
conda install statsmodels
conda install datashape
conda install seaborn
conda install -c conda-forge interpolation
conda install -c conda-forge awscli
conda install -c anaconda boto3
conda install -c r r-irkernel
```

@@

```{r}
# Install R-tools
install.packages("installr")
library("installr")
install.Rtools()
# c:/Rtools/bin;
# c:/Rtools/mingw_32/bin;
# c:/Rtools/mingw_64/bin;

@@

```{r}
# A simple file with summary statistics using tidyverse
source('C:/Users/fan/R4Econ/summarize/dist/fst_hist_onevar.R')
# Another simple file with summary statistics using tidyverse
source('C:/Users/fan/R4Econ/support/tibble/fs_tib_basics.R')
# A file involving estimation
source('C:/Users/fan/R4Econ/optimization/cesloglin/fst_ces_plan_linlog.R')
```

@@

- [git for windows](https://git-scm.com/download/win): after install, try "cd ~/PyFan"
- [atom](https://atom.io/)
- [pycharm](https://www.jetbrains.com/pycharm/)

>>>>

---
title: "New Windows Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations"
output:
  pdf_document:
    df_print: paged
    number_sections: true
  html_notebook:
    number_sections: true
  word_document:
    number_sections: true
  html_document:
    number_sections: true
urlcolor: blue
always_allow_html: yes
---

Go back to [fan](http://fanwangecon.github.io/)'s [Tex4Econ and Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/).

@@

See Anaconda Installation Directory, in anaconda prompt:

```{bash}
where anaconda
# C:/ProgramData/Anaconda3/Scripts/anaconda.exe
where python
# C:/ProgramData/Anaconda3/python.exe
where jupyter
# C:/ProgramData/Anaconda3/Scripts/jupyter.exe
where jupyter-kernelspec
# if R installed already
where r

###############################
# Add these to Windows PATH:
###############################
# C:/ProgramData/Anaconda3/Scripts
# C:/ProgramData/Anaconda3
```

@@

```{r}
conda install statsmodels datashape seaborn
# conda install statsmodels
# conda install datashape
# conda install seaborn

conda install -c conda-forge interpolation awscli
# conda install -c conda-forge interpolation
# conda install -c conda-forge awscli

conda install -c anaconda boto3

conda install -c r r-irkernel
```

@@

```{r}
# Install R-tools
install.packages("installr")
library("installr")
install.Rtools()
# c:\Rtools\bin;
# c:\Rtools\mingw_32\bin;
# c:\Rtools\mingw_64\bin;

@@

```{r}
# A simple file with summary statistics using tidyverse
source('C:/Users/fan/R4Econ/summarize/dist/fst_hist_onevar.R')
# Another simple file with summary statistics using tidyverse
source('C:/Users/fan/R4Econ/support/tibble/fs_tib_basics.R')
# A file involving estimation
source('C:/Users/fan/R4Econ/optimization/cesloglin/fst_ces_plan_linlog.R')

# C:\Users\fan\R4Econ\summarize\dist\fst_hist_onevar.Rmd
# C:\Users\fan\R4Econ\support\tibble\fs_tib_basics.Rmd
# C:\Users\fan\R4Econ\optimization\cesloglin\fst_ces_plan_linlog.Rmd
```

@@

- [pycharm](https://www.jetbrains.com/pycharm/)
